Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-24 paper.tex
improving introduction: Closes #16
removing some old-comments in the introduction: Closes #18
improving the SoA: Closes #15

In any case, the accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}. % This
                                % paragraph is rather useless - JJ
% I have changed the paragraph completely, but still don't know what
% this is doing here - JJ

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
%FERGU: some ... variables, no?
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
                                % do? What are the results?
% This is a state of the art? Are we already in the state of the art?
% - JJ

In the research published in this paper, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for bookshops,
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute
correct estimations (predictions), for instance, she can decide
increasing or decreasing the sales forecast based on season or sales
period.
However, carrying out the analysis and forecasting process as a human expert,
may lead to imprecise predictions which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}. A
initial version of this method was developed under contract with that
company and eventually integrated in their product. This paper
represents an improved version of that method based on the same data.

@@

In this case, just a few variables are known in advance
\cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
them are categorical, which makes them harder to process, even more so if the number
of categories is high. Given these issues, finding adequate
forecasting techniques and selecting  
the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj
% And it's the 3rd time you cite ChingChin!!! - JJ

>>>>

In any case, the accuracy of the predictive method we intend to design is affected
negatively by several factors, related to decisions on purchases, to freight 
traffic, or with the distribution strategy \cite{Little1998}.
Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
                                % do? What are the results?
% This is a state of the art? Are we already in the state of the art?
% - JJ

In the research published in this paper, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for bookshops,
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute
correct estimations (predictions), for instance, she can decide
increasing or decreasing the sales forecast based on season or sales
period.
However, carrying out the analysis and forecasting process as a human expert,
may lead to imprecise predictions which may not take all the variables into account. 
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{Sanders1994}. A
initial version of this method was developed under contract with that
company and eventually integrated in their product. This paper
represents an improved version of that method based on the same data.

@@

In this case, just a few variables are known in advance
\cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
them are categorical, which makes them harder to process, even more so if the number
of categories is high. As stated in those works, given these issues, finding adequate
forecasting techniques and selecting the best method to use is also a problem.
